Optimal Light Curve Attitude Inversion with Measurement Noise: Two Case Studies

### 2025-03-11 paper.tex
preparing for final writing bit

\begin{figure}[H]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_lcs_001_2_00x.png}
  \caption{Selected light curve for the Delta (Star-37E) rocket body, observed by the Purdue Optical Ground Station}
  \label{fig:rb_lc_obs}
\end{figure}

@@

@@

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=\figbig]{sphx_glr_plot_lcs_001_2_00x.png}
  \caption{Selected light curve for the Delta I (Star-37E) rocket body, observed by the Purdue Optical Ground Station}
  \label{fig:rb_lc_obs}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{sphx_glr_results_002_2_00x.png}
  \caption{Candidate solution inertia light curves compared to the real measurements in ADU for the Delta I (Star-37E) rocket body.}
  \label{fig:case2_s}
\end{figure*}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_001_2_00x.png}
  \caption{Candidate solution inertia ratio distribution for the Delta I (Star-37E) rocket body.}
  \label{fig:case2_i}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_006.png}
  \caption{Candidate solution orientation MRPs for the Delta I (Star-37E) rocket body.}
  \label{fig:case2_p}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_005.png}
  \caption{Candidate solution angular velocities for the Delta I (Star-37E) rocket body.}
  \label{fig:case2_w}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{sphx_glr_results_004_2_00x.png}
  \caption{Candidate solution inertia light curves compared to the real measurements in ADU for ECHOSTAR II.}
  \label{fig:case2_s}
\end{figure*}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_003_2_00x.png}
  \caption{Candidate solution inertia ratio distribution for ECHOSTAR II.}
  \label{fig:case2_i}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_008.png}
  \caption{Candidate solution orientation MRPs for ECHOSTAR II.}
  \label{fig:case2_p}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=\figmed]{sphx_glr_results_007.png}
  \caption{Candidate solution angular velocities for ECHOSTAR II.}
  \label{fig:case2_w}
\end{figure}

\section{Conclusion}
